A Data-Driven Framework for Neural Field Modelling

### 2010-11-19 ltx/first_order_framework/LaTeX_Manuscript.tex
miror corrections

\subsection{Implications for Experimental Design}
As seen in Fig.~\ref{fig:Figure7} and Fig.~\ref{fig:Figure9}, the results show good estimation accuracy for the connectivity kernels, where the true kernels lie within the 95~\% confidence intervals of the kernel estimates. The estimates of the connectivity kernels show relatively broad distributions over the different realisations, which can be expected considering the system's input is modelled as a random disturbance and the observations are corrupted by noise. To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings, where given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates would decrease. Even when using a known input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set. By designing an input signal carefully and using an evoked-potential paradigm where stimuli are repeated many times, recordings could be averaged over a sufficient number of trials (realisations), such that a distribution of the parameter estimates and resulting connectivity kernels can be formed.

>>>>

\subsection{Implications for Experimental Design}
As seen in Fig.~\ref{fig:Figure7} and Fig.~\ref{fig:Figure10}, the results show good estimation accuracy for the connectivity kernels, where the true kernels lie within the 95~\% confidence intervals of the kernel estimates. The estimates of the connectivity kernels show relatively broad distributions over the different realisations, which can be expected considering the system's input is modelled as a random disturbance and the observations are corrupted by noise. To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings, where given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates would decrease. Even when using a known input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set. By designing an input signal carefully and using an evoked-potential paradigm where stimuli are repeated many times, recordings could be averaged over a sufficient number of trials (realisations), such that a distribution of the parameter estimates and resulting connectivity kernels can be formed.
